---
title: "SUMMARY OF INFRACTIONS REPORTS RECEIVED BY THE COMMISSION"
subtitle: "Paper of information on infractions reported to the Secretariat"
author: "IWC Secretariat - Statistics and Modelling Department"
params: 
  first_year: 2021
  last_year: 2023
  membershipfile: "../inputs/NationsMembership.xlsx"
  infmasterfile: "../inputs/Infractions_master_table_SYNTHETIC.xlsx"
output: 
  word_document:
    reference_docx: word_styles.docx
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile,encoding = encoding,output_file = "infractions paper years x-x.docx",output_dir = "../outputs")})
---
Under the terms of the Convention, each Contracting Government is required to transmit to the Commission full details of each infraction of the provisions of the Convention committed by persons and vessels under the jurisdiction of the Government. 

Table 1 gives the reported percentage of catch under direct national inspection for the period `r params$first_year`-`r params$last_year`.

Table 2 gives a summary of the infractions reported for the period `r params$first_year`-`r params$last_year`.

Tables 3-`r (params$last_year - params$first_year)+4` give details of the infractions reported for the period `r params$first_year`-`r params$last_year`, per year. 

```{r setup, include=FALSE, echo = F}
#this report is needed when a Infractions subcommittee meeting takes place
#when the report is adopted through comment sheets and correspondence other reports might be more useful.
knitr::opts_chunk$set(echo = FALSE)
library(flextable)
library(dplyr)
library(tidyverse)
library(readxl)
library(officer)
library(plyr)
library(dplyr)
library(magrittr)

FitFlextableToPage <- function(ft, pgwidth = 6){
  ft_out <- ft %>% autofit()
  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}

#read in the membership dates
members <- read_excel(params$membershipfile)
members$DateIn <- as.Date(members$EIFdate, "%B %d, %Y")
members$DateOut <- as.Date(members$withdrawal, "%B %d, %Y")
members$DateOut[is.na(members$DateOut)] <- Sys.Date()

years <- params$first_year:params$last_year

```
```{r infractionsmain, echo = F, results='asis', warning=FALSE, message=FALSE}
#read in the raw data
column_names <- names(
  read_excel(params$infmasterfile, sheet = 1, n_max = 0)
)

col_types <- rep("guess", length(column_names))

col_types[
  column_names == "Percentage of catch under direct national inspection"
] <- "text"

infractions <- read_excel(
  params$infmasterfile,
  sheet = 1,
  col_types = col_types
)

whichismember1 <- function(x = infractions, members = members){
  #when no info for date columns fill in the values
  x$date[is.na(x$date)] <- as.Date(paste(x$Year[is.na(x$date)],"01","01", sep="-"), "%Y-%m-%d")

  x$Member <- NA
  
  for (i in 1:nrow(x)){
    #find the right country in the members table
    indm <- which(members$Participant == x$Nation[i])
    if(length(indm) != 0){
    memberSD <- max(members$DateIn[indm])
    memberED <- max(members$DateOut[indm])
    if (x$date[i] <= memberED & x$date[i] >= memberSD){
      x$Member[i] <- 'Members'
      } else {
      x$Member[i] <- 'Non Members'
    }
    } else {
      x$Member[i] <- 'Non Members'
      }
  }
  return(x)
}
#member and non member nations
infractionsM <- whichismember1(x = infractions, members = members)
#select only member nations
infractionsM <- infractionsM[infractionsM$Member == "Members",]

#length
infractionsM$lengthU <- paste(infractionsM$length, infractionsM$length_unit, sep = " ")

#choose the years of interest
infractionsperiod <- infractionsM[infractionsM$Year %in% years,]

#choose only the large whales
infractionsL <- infractionsperiod[infractionsperiod$group == "large cetaceans",]

#make a table that sums up individuals takes by infractions, including 0
infractionsA <- aggregate(number  ~ Year+Member+Nation+species, infractionsL, sum)
infractionsA <- infractionsA[order(infractionsA$Year,infractionsA$Nation),c('Year','Member','Nation', 'species', 'number')]
infractionsA$species[which(infractionsA$species == "all")] <- "infractions reported"
infractionsA$InfReported <- paste0(infractionsA$number," " ,infractionsA$species)
#select only the columns necessary for the 1st table
infractionsA1 <- infractionsA[,c('Year', 'Nation',"InfReported")]
infractionsA1 <- aggregate(data=infractionsA1,InfReported~.,FUN=paste,collapse=" , ")
#make year a column
infractionsAW <- reshape(infractionsA1, idvar = c('Nation'), timevar ='Year', direction = "wide")
infractionsAW <- as.data.frame(infractionsAW)
infractionsAW <- infractionsAW[order(infractionsAW$Nation),]
colnames(infractionsAW) <- c("Nation", as.character(years))
for (i in as.character(years)) infractionsAW[is.na(infractionsAW[,i]),i] <- ""

#info on small cetaceans included in the infractions reports
infractionssmalls <- infractionsperiod[infractionsperiod$group == "small cetaceans",]
if (nrow(infractionssmalls) >0){
infractionsA <- aggregate(number  ~ Year+Member+Nation+species, infractionssmalls, sum)
infractionsA <- infractionsA[order(infractionsA$Year,infractionsA$Nation),c('Year','Member','Nation', 'species', 'number')]
infractionsA$InfReported <- paste0(infractionsA$number," " ,infractionsA$species)
infractionsA1 <- infractionsA[,c('Year', 'Nation',"InfReported")]
infractionssmalls1 <- aggregate(data=infractionsA1,InfReported~.,FUN=paste,collapse=" & ")
infractionssmalls1$infractionsS <- paste("in ",infractionssmalls1$Year," ",infractionssmalls1$Nation," reported ",infractionssmalls1$InfReported)
SmallCetaceansFootnote <- paste0("The following small cetaceans catches were reported in the infractions reports: ",paste(infractionssmalls1$infractionsS,collapse = "; "))
} else {
 SmallCetaceansFootnote <- NA 
}

#tables of detailed infractions
infractions0 <- infractionsL[infractionsL$number>0,]
infractionsB <- infractions0[order(infractions0$Year,infractions0$Member,infractions0$Nation, infractions0$species),c('Year','Member','Nation', 'species', 'number', 'sex','lengthU','infraction', 'details', 'penalty')]
colnames(infractions0)[which(colnames(infractions0) == 'lengthU')] <- 'length'
infractionsBL <- split(infractionsB, infractionsB$Year)

#percentage of catch under national inspection
# percentage of catch under national inspection
inspection_col <- "Percentage of catch under direct national inspection"

infractionsperiod[[inspection_col]][
  infractionsperiod[[inspection_col]] == "NA"
] <- NA

infractionsInspect <- infractionsperiod[
  !is.na(infractionsperiod[[inspection_col]]),
  c("Year", "Nation", inspection_col)
]

infractionsInspect <- infractionsInspect[,c("Year", "Nation", inspection_col)]

x <- infractionsInspect[[inspection_col]]

x_num <- suppressWarnings(as.numeric(x))

is_number <- !is.na(x_num)

x[is_number] <- paste0(
  format(
    x_num[is_number] * 100,
    trim = TRUE,
    scientific = FALSE
  ),
  "%"
)

infractionsInspect[[inspection_col]] <- x

infractionsInspect <- aggregate(data=infractionsInspect,`Percentage of catch under direct national inspection`~.,FUN=function(x) {return(x[1])})

infractionsInspect$Year <- as.character(infractionsInspect$Year)
```

```{r percentinspection, echo = F, results='asis', warning=FALSE, message=FALSE}

flextable_to_rmd(flextable(infractionsInspect) %>% 
  theme_booktabs() %>%
    bold( bold = TRUE, part="header") %>% 
     set_caption(
      caption = paste0(
        "Table 1. Percentage of catch under direct national inspection, reported for the period ",
        min(years), "–", max(years), "."
      ),
      autonum = officer::run_autonum(
        seq_id = "tab",
        pre_label = "Table ",
        post_label = ". "
      )
    ) %>%
  #FitFlextableToPage(pgwidth = 10) %>%
    fontsize(size = 9, part = "all") %>%
    font(fontname = "Times", part = "all") %>%
    autofit(part = "all") %>%
    align(align = "center", part = "all") %>% 
    merge_v(j = c("Nation", "Percentage of catch under direct national inspection"))%>%
    border_inner_h(border = fp_border(color="gray", width=1))
)
cat("\n  <br>  \n")

```

```{r infractionssummary, echo = F, results='asis', warning=FALSE, message=FALSE}
if (is.na(SmallCetaceansFootnote)){
flextable_to_rmd(as_grouped_data(infractionsAW, groups = c("Nation")) %>% 
  as_flextable(hide_grouplabel = TRUE) %>% 
  #add_footer_lines("Observed event") %>%
  #set_header_labels(what = "") %>% 
  #color(part = "footer", color = "#800000") %>%
  theme_booktabs() %>%
    bold( bold = TRUE, part="header") %>% 
    set_caption(caption = paste0("Table 2. Summary of the total number of individual large whales taken as infractions, reported for the period ",min(years),"-",max(years),". Reported 0 infractions are included.")) %>%
  FitFlextableToPage(pgwidth = 10) %>%
    fontsize(size = 9, part = "all") %>%
    font(fontname = "Times", part = "all") %>%
    autofit(part = "all") %>%
    align(align = "center", part = "all") %>% 
    align(i = ~ !is.na(Nation), align = "left") %>%
    bold(i = ~ !is.na(Nation)) %>%
    border_inner_h(border = fp_border(color="gray", width=1))
) 
  } else {
  flextable_to_rmd(as_grouped_data(infractionsAW, groups = c("Nation")) %>% 
  as_flextable(hide_grouplabel = TRUE) %>% 
  add_footer_lines(SmallCetaceansFootnote) %>%
  set_header_labels(what = "") %>% 
  color(part = "footer", color = "dark grey") %>%
  bold( bold = TRUE, part="header") %>% 
    set_caption(caption = paste0("Table 2. Summary of the total number of individual large whales taken as infractions, reported for the period ",min(years),"-",max(years),". Reported 0 infractions are included.")) %>%
  FitFlextableToPage(pgwidth = 6) %>%
    fontsize(size = 9, part = "all") %>%
    font(fontname = "Times", part = "all") %>%
    theme_booktabs() %>%
    autofit(part = "all") %>%
    align(align = "center", part = "all") %>% 
    align(i = ~ !is.na(Nation), align = "left") %>%
    bold(i = ~ !is.na(Nation)) %>%
    border_inner_h(border = fp_border(color="gray", width=1))
  )
}

cat("\n  <br>  \n")


```

```{r infractionstables, echo = F, results='asis', warning=FALSE, message=FALSE}
for (y in 1:length(years)){
dfB <- infractionsBL[[paste(years[y])]]
dfB$Member <- NULL
if(length(dfB) > 0){
dfB$Year <- NULL
flextable_to_rmd(as_grouped_data(dfB, groups = c("Nation", "species")) %>% 
  as_flextable(hide_grouplabel = TRUE) %>% 
  theme_booktabs() %>%
    bold( bold = TRUE, part="header")  %>%
    set_caption(caption = paste0("Table ", y + 2,"Details on reported infractions for the ",years[y]," season. U: unknown.")) %>%
  FitFlextableToPage(pgwidth = 11) %>%
    fontsize(size = 9, part = "all") %>%
    font(fontname = "Times", part = "all") %>%
    align(align = "center", part = "all") %>% 
    width(width = 1.4) %>%
    width(j = "details", width = 4, unit = "in") %>% 
    width(j = "infraction", width = 2, unit = "in")%>% 
  align(i = ~ !is.na(species), align = "left") %>% 
  bold(i = ~ !is.na(species))%>% 
  align(i = ~ !is.na(Nation), align = "left") %>% 
  bold(i = ~ !is.na(Nation)) %>%
    border_inner_h(border = fp_border(color="gray", width=1))
)

cat("\n  <br>  \n")}
}
```
